A Combinatorial Search of Parameterized Quantum Circuit Learning for Chemical Applications

### 2024-11-21 manuscript/main.tex
Thu 21 Nov 2024 16:22:11 EST update

\newpage
\textcolor{red}{Reorganize}
\begin{itemize}
	\item Abstract
	\item Introduction
	\item Methods
	\item Datasets
	\item Results
	\begin{itemize}
		\item Function fitting 
		\begin{itemize}
			\item Classical testing
			\item All (5 + 16 qubit)
			\item RUD + AL (5 + 16 qubit)
			\item Error mitigation
			\item Real device
		\end{itemize}
		\item DDCC (5 qubit only because classically it can be done with 5 features!)
		\begin{itemize}
			\item Classical testing
			\item Truncated  5 qubit set (based on BSE 5 qubit cost analysis)
			\item RUD + AL (5)
			\item Error mitigation
			\item Real device
		\end{itemize}
		\item BSE
		\begin{itemize}
			\item Classical testing
			\item All 5 qubit
			\item Truncated 16 qubit set (cost analysis 5 qubit)
			\item RUD + AL (5 + 16 qubit)
			\item Error mitigation
			\item Real device
		\end{itemize}				
	\end{itemize}
	\item Discussion and Conclusion
\end{itemize}

\newpage
\section{Introduction}
\cite{prasad_applications_2024}
\cite{suzuki_predicting_2020}
\cite{mitarai_quantum_2018}
\cite{sim_expressibility_2019}
\cite{hatakeyama-sato_quantum_2023}
\cite{krenn_artificial_2023}
\cite{benedetti_parameterized_2019}
\cite{biamonte_quantum_2017}

>>>>

\newpage
\begin{itemize}
	\item Abstract
	\item Introduction
	\item Methods
	\item Datasets
	\item Results and Discussion
	\begin{itemize}
		\item Function fitting 
		\begin{itemize}
			\item All (5 + 16 qubit)
			\item RUD + AL (5 + 16 qubit)
			\item Error mitigation on FakeQuebec
		\end{itemize}
		\item BSE
		\begin{itemize}
			\item All 5 qubit
			\item Truncated 16 qubit set (cost analysis 5 qubit)
			\item RUD + AL (5 + 16 qubit)
			\item Real device (without error mitigation and with whatever the best is from function fitting)
		\end{itemize}		
		\item DDCC (5 qubit only because classically it can be done with 5 features!)
		\begin{itemize}
			\item Truncated  5 qubit set (based on BSE 5 qubit cost analysis)
			\item RUD + AL (5 qubit)
			\item Real device (without error mitigation and with whatever the best is from function fitting)
		\end{itemize}				
	\end{itemize}
	\item Conclusion
\end{itemize}

\newpage
\section{Introduction}
\cite{prasad_applications_2024}

A1, A2, M-Encoding \cite{suzuki_predicting_2020}
M-Encoding \cite{mitarai_quantum_2018}

Ansaetze \cite{sim_expressibility_2019}
``In particular, a substantial improvement in performance of two-qubit gates in a ring or all-to-all connected arrangement, compared to thatof those on a line, is observed.''

``Furthermore, improvement in both descriptors is achieved by sequences of controlled X-rotation gates compared tosequences of controlled Z-rotation gates.''

``investigated howexpressibility “saturates” with increased circuit depth, finding that the rateand saturated value appear to be distinguishing features of a PQC''

IQP \cite{bremner_average-case_2015}

\cite{hatakeyama-sato_quantum_2023}
\cite{krenn_artificial_2023}
\cite{benedetti_parameterized_2019}
\cite{biamonte_quantum_2017}
